Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-27 Latex/tex/pr.tex
12233

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}   
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\begin{document}

@@

\section{Introduction}
O-RAN, which is the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G Network, to enhance RAN performance.  
The idea of O-RAN comes from two opinions. Firstly, according to real-time analytic used for artificial intelligence systems, the radio access networks must be evolved to be more intelligent and flexible than before. Also O-RAN uses deep learning techniques to develop smarter layers in its architecture.
 Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces.
In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms, in order to be more flexible for mobile network operators MNOs especially for mobile virtual network operators (MVNOs)\cite{oran1}. 
Openness is the specific feature of O-RAN. Open interface is one of the most crucial properties for O-RAN to enable MNOs and MVNOs, to define their own services.
The concept of software defined network (SDN), which is the separation of control plane (CP), from user plane (UP), is deployed in an intelligent O-RAN architecture. The seperation of CP/UP is developed  through the E1 interface. Moreover, this separation, promote RRM by defining Non-RT
and Near-RT) RAN Intelligent Controller (RIC) with the A1 and E2 interfaces .
O-RAN introduced interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
(RIC non-RT) function and the eNB/gNB containing the near-real-time RIC
(RIC near-RT) function.\cite{oranpaper}

@@

The rest of the paper is organized as follows. In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical resources is expressed. Also, problem statements is explained and decomposed to two
different sub-problems. 
In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results, is depicted for the sub-problems.

@@

In this section, first, we first present the system model, Then we obtain achievable rates and delays for the downlink (DL) of the O-RAN architecture.
Afterward, the main problem is expressed.

@@

Suppose we have two processing layers in the BBU-Pool of O-RAN system which contain VNFs. The lower layer consist of high-PHY and MAC, and the upper layer consist of RLC, PDCP and SDAP.

@@

To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service which is given by \eqref{eq3}

@@

where, $a_{v,s}$ is a binary variable denotes which the slice $s$ is mapped to service $v$ or not .

@@

It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs equally. Each dispatcher first processes the incoming traffic and divides equally to each VNF  \cite{frdl,luong2018novel,luong2018novel1}.

@@

d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}} \\
d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}.

@@

where, $\mu_1$ and $\mu_2$ is the computational capacity of the first and the second layer respectively.
In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission
 is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice divide traffic data and transmit divided traffic to VNFs.

@@

 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1}. Therefore, 

@@

Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$.

@@

physical resources that contain RAM, Memory, and CPU.
Let, the required resources for VNF $f$ in slice $s$ is represented by a three-dimensional vector as follow

@@

\bar{\Omega}_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \};

@@

Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory, and CPU, respectively.
Moreover total amount of required RAM, Memory, and CPU of all VNFs of a slice is a three-dimensional vector which is defined as

@@

\bar{\Omega}_{s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{(f,s)};

@@

Also, there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's requirements.
The amount of RAM, Memory, and CPU is denoted by $\tau_{R_{j}}, \tau_{M_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively.

@@

\tau_j = \{\tau_{R_{j}}, \tau_{M_{j}}, \tau_{C_{j}} \};

@@

Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ is the weight of RAM, Memory, and CPU that is used for Algorithm \ref{alg3}.

@@

One of the most important parameters to estimate the optimality of the system is energy efficiency which is represented as a sum-rate to sum-power 

@@

Where, $\sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices. Also, $\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services. 

@@

\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d}.

@@

In this paper, the main goal is to maximize sum-rate and minimize sum-power (the total power of all RRHs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow, 

@@

\section{Simulation}\label{simul}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}   
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\begin{document}

@@

\section{Introduction}
O-RAN, which is the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G Network, to enhance RAN performance.  
The idea of O-RAN comes from two opinions. Firstly, according to real-time analytic used for artificial intelligence systems, the radio access networks must be evolved to be more intelligent and flexible than before. Also O-RAN uses deep learning techniques to develop smarter layers in its architecture.
 Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces.
In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms, in order to be more flexible for mobile network operators MNOs especially for mobile virtual network operators (MVNOs)\cite{oran1}. 
Openness is the specific feature of O-RAN. Open interface is one of the most crucial properties for O-RAN to enable MNOs and MVNOs, to define their own services.
The concept of software defined network (SDN), which is the separation of control plane (CP), from user plane (UP), is deployed in an intelligent O-RAN architecture. The seperation of CP/UP is developed  through the E1 interface. Moreover, this separation, promote RRM by defining Non-RT
and Near-RT) RAN Intelligent Controller (RIC) with the A1 and E2 interfaces.
O-RAN introduced interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
(RIC non-RT) function and the eNB/gNB containing the near-real-time RIC
(RIC near-RT) function \cite{oranpaper}.

@@

The rest of the paper is organized as follows. In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is expressed. Also, problem statements is explained and decomposed to two
different sub-problems. 
In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results, is depicted for the sub-problems.

@@

In this section, first, we first present the system model, Then we obtain achievable rates and delays for the downlink (DL) of the O-RAN architecture. Afterward, we explained physical data center resources.
Finally, the main problem is expressed.

@@

Suppose we have two processing layers in the BBU-Pool of O-RAN system which contain VNFs. The lower layer consist of high-PHY, MAC, and RLC, and the upper layer consist of RRC, PDCP and SDAP.

@@

To obtain SNR as formulated in \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service

@@

where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .

@@

It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs equally. The dispatcher processes the incoming traffic and divides it equally to processed by VNFs  \cite{frdl,luong2018novel,luong2018novel1}.

@@

d_{s_1} &= \frac{1}{\mu_1 - \alpha_{s}/{M_{s,1}}} \\
d_{s_2} &= \frac{1}{\mu_2 - \alpha_{s}/{M_{s,2}}}.

@@

where, $1/\mu_1$ and $1/\mu_2$ are the mean service time of the first and the second layer respectively, due to the fact that the service time of each data packet has an exponential distribution for $\mu_i>\alpha_{s}/{M_{s,i}}$ $ i \in \{1,2\}$.
In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission . The arrival data rate of wireless transmission
 is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice \cite{frdl}.

@@

 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore, 

@@

where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$ is the total achievable rate of each slice that is mapped to specific service.

@@

physical resources that contain memory, storage and CPU.
Let the required resources for VNF $f$ in slice $s$ is represented by a three-dimensional vector as follow

@@

\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f \};

@@

where, $\bar{\Omega}_{s}^f\in \mathbb{C}^{3}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, storage, and CPU, respectively.
Moreover the total amount of required memory, storage and CPU of all VNFs of a slice is a three-dimensional vector which is defined as

@@

\bar{\Omega}_{\mathfrak{z},s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{\mathfrak{z},s}^f \;\; \mathfrak{z} \in \{M, S, C\};

@@

Also, there are $D_c$ data centers (DC), serving VNFs. Each DC contains several servers that supply VNF's requirements.
The amount of memory, storage and CPU is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively.

@@

\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}} \};

@@

Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ is the weight of memory, storage and CPU that is used for Algorithm \ref{alg3}.

@@

One of the most important parameters to measure the optimality of the system is energy efficiency which is represented as a sum-rate to sum-power 

@@

where, $\sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices. Also, $\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services. 

@@

\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi_{s,d} - \E{[\phi]}\sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} .

@@

Our goal is to maximize sum-rate and minimize sum-power (the total power of all RRHs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow, 

@@

\section{Numerical Results}\label{simul}
